2024 US Presidential Election Model

### 2024-10-20 paper/paper.qmd
committing changes to rendered file
commit changes

\[
\begin{align}
y_i | \mu_i &\sim \text{Bernoulli}(\mu_i) \\
\mu_i &= \alpha + \beta_i + \gamma_i \\
\alpha &\sim \text{Normal}(0, 2.5) \\
\beta_i &\sim \text{Normal}(0, 2.5) \\
\gamma_i &\sim \text{Normal}(0, 2.5)
\end{align}
\]

@@

The model used to predict the 2024 US Presidential Election outcome is a logistic regression model. The binary outcome variable, \( y_i \), represents whether Donald Trump (1) or Kamala Harris (0) is predicted to win each state. The predictor variables, \( \beta_i \) and \( \gamma_i \), are the average polling percentages for Trump and Harris, respectively, in state \( i \). We use a logistic regression model because the outcome is binary, making it appropriate for estimating the probability of a Trump victory in each state. The model is implemented in R using the `glm()` function with a binomial family, providing a probabilistic prediction of the election outcome based on polling data.

@@

We expect a positive relationship between polling support for each candidate and the likelihood of winning a state. In particular, as the percentage of support for Donald Trump (\(\beta_i\)) increases, the probability of Trump winning state \(i\) also increases. Similarly, as Kamala Harris's support (\(\gamma_i\)) increases, the likelihood of her winning the state rises. The logistic regression model is suitable for capturing these dynamics, as it allows us to estimate the probability of a binary outcome (win or lose) using continuous predictor variables. The model outputs probabilities that are constrained between 0 and 1, which aligns with the binary nature of our outcome variable (\(y_i\)). In essence, we expect a higher \(\beta_i\) to correlate with a higher probability of Trump winning a state, while a higher \(\gamma_i\) suggests a greater likelihood of a Harris victory.

>>>>

\begin{align*}
y_i | \mu_i &\sim \text{Bernoulli}(\mu_i) \\
\mu_i &= \alpha + \beta_i + \gamma_i \\
\alpha &\sim \text{Normal}(0, 2.5) \\
\beta_i &\sim \text{Normal}(0, 2.5) \\
\gamma_i &\sim \text{Normal}(0, 2.5)
\end{align*}

@@

The model used to predict the 2024 US Presidential Election outcome is a logistic regression model. The binary outcome variable, $y_i$, represents whether Donald Trump (1) or Kamala Harris (0) is predicted to win each state. The predictor variables, $\beta_i$ and $\gamma_i$, are the average polling percentages for Trump and Harris, respectively, in state $i$. We use a logistic regression model because the outcome is binary, making it appropriate for estimating the probability of a Trump victory in each state. The model is implemented in R using the `glm()` function with a binomial family, providing a probabilistic prediction of the election outcome based on polling data.

@@

We expect a positive relationship between polling support for each candidate and the likelihood of winning a state. In particular, as the percentage of support for Donald Trump ($\beta_i$) increases, the probability of Trump winning state $i$ also increases. Similarly, as Kamala Harris's support ($\gamma_i$) increases, the likelihood of her winning the state rises. The logistic regression model is suitable for capturing these dynamics, as it allows us to estimate the probability of a binary outcome (win or lose) using continuous predictor variables. The model outputs probabilities that are constrained between 0 and 1, which aligns with the binary nature of our outcome variable ($y_i$). In essence, we expect a higher $\beta_i$ to correlate with a higher probability of Trump winning a state, while a higher $\gamma_i$ suggests a greater likelihood of a Harris victory.
